|

### 2020-04-03 Paper-2020.Rmd
Includes submitted JOPskeleton

Since the 1970s, the U.S. Supreme Court has maintained that nearly all limits on political spending violate the first amendment’s protection of free speech. In its 1976 _Buckley v. Valeo_ decision, the Court laid out only two admissible justifications for limiting campaign donations: To prevent corruption or the appearance of corruption. But do campaign finance limits actually prevent corruption or its appearance? As current challenges to contribution limits wind their way through federal courts, the answer to this question will inform the Supreme Court’s decision to uphold or strike down remaining limits on political campaign contributions. Using state-level data from 1990-2012 on contribution limits, corruption convictions, and media mentions of corruption, this paper employs linear panel regressio to test whether campaign contribution limits are associated with lower levels of corruption convictions or media mentions of corruption. These methods find associations between corruption convictions and the presence of limits on donations to political action committees (PACs), the amount of those limits, and the presence of limts on donations to parties. Applying these methods to recently developed measures of media mentions of corruption suggests that these data may require further development.[^SPSA]

@@

```{r Barber summary stats latex, results="asis",eval=T,include=F}
# This is what fails to knit (see error below) 
stargazer(as.data.frame(subset(BarberNAs[,3:6])), digits=0, type="latex", title="Descriptive Statistics for State Level Campaign Finance Limits", covariate.labels = c("Individual Limits","Individual-to-Party Limits","Party Limits", "PAC Limits"), header=F, 
          notes = "Notes: 'N' equals number of state-years (out of n=1150) in which that type of limit is present") 
```

@@

The fourth data set provides controls for the panel model. In their 2012 work examining variation in prosecutorial resources, Alt and Lassen follow Glaeser and Saks (2006) in controlling for income and education levels, size of government, legislature control, and urbanization (see Appendix X). Alt and Lassen's data set runs from 1976-2004. When included in the second and third models, this limits the analysis to the years from 1990-2004 and n=720.

@@

#### Corruption Convictions Index versus campaign contribution limits in a given state-year: 
$(log)Convictions = \alpha_{state} + \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}*{indiv.limit} + \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}*{pac.limit} + \beta_{5}{indiv-to-party.dummy} + \beta_{6}{indiv-to-party.dummy}*{indiv-to-party.limit} + Controls + \epsilon$

#### Corruption Reflections Index versus campaign contributions in a given state-year: 
$(log)Reflections = \alpha_{state} + \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}*{indiv.limit} + \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}*{pac.limit} + \beta_{5}{indiv-to-party.dummy} + \beta_{6}{indiv-to-party.dummy}*{indiv-to-party.limit} + Controls + \epsilon$

##Results

@@

cci.log.iv.fixed.time <- plm(log(CCI+1) ~ 
           ind_limits_2010*ind_limits_dummy 
           + ind2pty_limits_2010*ind2pty_limits_dummy 
           + pac_limits_2010*pac_limits_dummy
           + jdiv  # Divided government 
           # + bindingonetermlimit # Binding one-term limit 
           # + bindingtwotermlimit # Binding two-term limit 
           # + rpcinc_annual_new # Real per capita income ($1000)
           + eopop # AUSAs per million population
           # + unemp # Unemployment 
           # + citi6006 # Citizen ideology measure 
           + high_school + # Percent high school graduates
           + rgenrevpc # Real per capita gov revenues ($1000)
           # + men_ineqincwag # Inequality: Male wages
           # + grelimp # Relative government wages
           + urbanization_2 # Urbanization 
           + logpop, # Log of population (millions)
           data = AltBarber, 
           model="within",
           effect="twoways")

@@

```{r CCI models output, eval=T,results="asis"}
stargazer(
  cci.log.pars, 
  cci.log.iv, # F Stat down? 
  cci.log.iv.log, # F Stat down further 
  #cci.log.iv.fixed, # AR2 Stat bottoms out 
  cci.log.iv.fixed.time, 
  type="latex",
  #out = "collateral/test.htm",
  font.size = "small",
  header=FALSE, 
  column.sep.width = "-15pt", 
  digits = 2, digits.extra = 0, 
  no.space = TRUE,
  title = "Models of Contribution Limits and Corruption Convictions",
  dep.var.labels = "Corruption Convictions Index (logged)",
  covariate.labels=c("Individual limit (amount)",
                     "Individual limit (logged)",
                     "Individual limit (dummy)",
                     "Individual-to-party limit (amount)",
                     "Individual-to-party limit (logged)",
                     "Individual-to-party limit (dummy)",
                     "PAC limit (amount)",
                     "PAC limit (logged)",
                     "PAC limit (dummy)",
                     "Divided government",
                     "AUSAs per population (MMs)"),
                     # "% high school grads",
                     # "Govt revenues/capita ($1000s)",
                     # "Urbanization",
                     # "Log of population (MMs)"),
  add.lines = list(c(" ","Base Model","With IVs","Pooled","FE"))
  )

@@

cri.log.iv.fixed.time <- plm(log(CRI+1) ~ 
             ind_limits_2010*ind_limits_dummy 
           + ind2pty_limits_2010*ind2pty_limits_dummy 
           + pac_limits_2010*pac_limits_dummy
           # jdiv  # Divided government 
           # + bindingonetermlimit # Binding one-term limit 
           # + bindingtwotermlimit # Binding two-term limit 
           # + rpcinc_annual_new # Real per capita income ($1000)
           + eopop # AUSAs per million population
           # + unemp # Unemployment 
           + citi6006 # Citizen ideology measure 
           + high_school + # Percent high school graduates
           + rgenrevpc # Real per capita gov revenues ($1000)
           + men_ineqincwag # Inequality: Male wages
           # + grelimp # Relative government wages
           + urbanization_2 # Urbanization 
           + logpop, # Log of population (millions)
           data = AltBarber, 
           model="within",
           effect="twoways")

@@

```{r CRI models output, eval=T,results="asis"}
stargazer(
  #cri, # started here, with other peoples' models 
  #cri.log, # Logged DVs; better results
  cri.log.pars, # Slimmed down model, no explanatory power lost 
  cri.log.iv, # Adding in IVs. AR2 up, F Stat down 
  cri.log.iv.log, # Logging IVS. AR2 down, F Stat down 
  #cri.log.iv.fixed, # AR2 to zero 
  cri.log.iv.fixed.time, # AR2 now negative 
  type="latex",
  #out = "collateral/test.htm",
  font.size = "small",
  header=FALSE, 
  column.sep.width = "-15pt", 
  digits = 2, digits.extra = 0, 
  no.space = TRUE,
  title = "Models of Contribution Limits and Corruption Reflections",
  dep.var.labels = "Corruption Reflections Index (logged)",
  covariate.labels=c("Individual limit (amount)",
                     "Individual limit (logged)",
                     "Individual limit (dummy)",
                     "Individual-to-party limit (amount)",
                     "Individual-to-party limit (logged)",
                     "Individual-to-party limit (dummy)",
                     "PAC limit (amount)",
                     "PAC limit (logged)",
                     "PAC limit (dummy)",
                     "AUSAs per million population",
                     "Citizen ideology measure",
                     "Percent high school graduates",
                     "Real per capita gov revenues (1000s)",
                     "Inequality: Male wages","Urbanization",
                     "Log of population (millions)"),
  add.lines = list(c(" ","Base Model","With IVs","Pooled","FE"))
  )

@@

### Modeling campaign limits and corruption convictions 
The results of the panel regressions reveal no correlation between state-level campaign contribution limits and corruption, with one exception: There is a statistically significant relationship between the presence of individual-to-party limits and the Corruption Reflections Index.

The first set of models (Table X) measures the association of various campaign contribution limits with the Corruption Convictions Index. The first model includes only control variables; the second model adds in campaign finance limit variables. The third layers in fixed effects at the state level, and the fourth incorporates fixed time effects. Not included are random effects models, which showed no improvement in the models. None of those results are significant at the p<0.05 level, implying that we cannot claim their effect is distinguishable from no effect. I interpret these results as showing no relationship between the presence or amount of state-level contribution limits and levels of corruption as measured by the Corruption Convictions Index.

The second set of models (Table X) also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.11 point decline in the Corruption Reflections Index. The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), indicating that the presence of individual-to-party limits is associated with a 11% decrease in the index.

## Discussion
At least one group of models allows for a straightforward interpretation. The panel models examining the relationship between state-level campaign finance laws and the Corruption Convictions Index fail to show any correlation between state level campaign finance laws and levels of corruption as measured by corruptions convictions, even controlling for variation in enforcement across the states.

The results for the models examining the relationship between campaign finance limits and the Corruption Reflections Index are less clear. The pair of stars in the fourth model suggest that the presence of individual-to-party limits is associated with a decrease in the Corruption Reflections Index. There is a less than 1% probability that the results are due to chance. How could this be, given that (a) the presence of individual-to-party limits has no association with a change the Corruption Convictions Index; (b) none of the other contribution limits are associated with a change in the Corruption Reflections Index; and (c) there is no correlation between the dollar amount of the individual-to-party limit and the Corruption Reflections Index? In practice, this would mean that states with individual-to-party limits also see lower levels of Associated Press reporting on corruption, but that once limits of any kind are imposed, the level of limit does not matter. It would also mean that only individual-to-party limits matter, not individual-to-candidate or PAC-to-candidate limits. Lastly, it would imply that the presence of such limits has an effect on reporting about corruption, but not on corruption convictions.

There is limited theoretical explanation for this outcome. It could be that AP reporters are somehow more likely to report on conviction allegations against political parties than against individual candidates or PACs, even where those allegations don’t result in greater levels of convictions, and only in states where the absence of contribution limits allows for a clean, “no limits on contributions” narrative. It is more likely, however, that these results call into question the robustness of Dincer and Johnston’s Corruption Reflections Index. As mentioned above, further research could carry forward their text-mining method into a greater number and variety of outlets, in order to find a measure of corruption reporting more tightly correlated with other measures.

## Conclusion
There at least two distinct and opposing ways to explain these results, viewpoints that will come into direct and public conflict if the Court chooses to hear a first amendment challenge to campaign contribution limits.

The first interpretation is that campaign finance and quid pro quo corruption are simply not related. How could this be? One explanation is that the measures of corruption used here fail to capture most corruption, which is never prosecuted. This explanation, however, would rest on the assumption that corruption is unequally captured across states over time. A second explanation is that corruption occurs regardless of campaign finance laws: Politicians likely to engage in corrupt behavior will do so outside of the campaign finance regime, where their transactions would be most visible.

The legal implications of this interpretation are clear and material. The Supreme Court presently equates political donations with political speech, meaning that it is protected by the first amendment, but that preventing corruption or its appearance in the political system is so important that first amendment rights can be abridged to ensure it. For the Court, no other justification--including creating a more informed electorate, or stimulating more competitive elections, or equality of financial participation in elections--is an important enough concern that we should limit political speech in the form of campaign donations. If there is no link between campaign contribution limits and corruption,  the Court may conclude that there is no reason to abridge US citizens’ first amendment rights by limiting campaign donations.

In order to make this anti-reform argument, some important limitations must be dealt with. First, the Corruptions Conviction Index used above has multiple issues, as summarized above. Second, Dincer and Johnston’s Corruption Reflections Index, while a worthy effort, needs to be developed further. It relies on a single news source; a second version could examine state-level reporting, or include outlets from across the political spectrum. Second, the Corruption Reflections Index carries with it the assumption that media mentions are a mere reflection of corruption, whereas other work has demonstrated that media reporting on corruption has its own biases, and its own effects on perceptions of corruption. Further research could more fully explore these relationships, including the manner in which public perceptions of corruption provide enabling or constraining environments for corruption itself. Given the importance of these limitations, all that can be concluded from the analysis above is that no link between contribution limits and corruption has been demonstrated with this data, not that no link exists.

@@

If Jim Bopp and other conservative legal scholars have their way, the Supreme Court will soon take a closer look at the logic laid out by their predecessors in 1976 in support of campaign contribution limits. Justice Thomas's comments in _McCutcheon v. FEC_ suggest that commitment to the Buckley v. Valeo structure is weakening, and not in the way that campaign finance reformers might hope. Despite effort, scholars have failed to provide compelling evidence of a link between campaign contribution limits and corruption as defined by the Court. The measures of corruption that academics have used to date have serious limitations. Yet if the Court decides the burden of proof is on those looking to restrict political spending on narrow corruption grounds, reform advocates worried about money in politics have a steep empirical hill to climb, and likely only a few short years to do it.

##Appendix X: Descriptions and Descriptive Statistics of Control Variables 
In their 2012 paper "Enforcement and Public Corruption: Evidence from the American States," Glaeser and Saks make use of the following control variables, which we have included here:

@@

##References 
<!--Add new authors (see Google doc) and data. R packages?-->
Ansolabehere, Stephen, John M de Figueiredo, and James M Snyder Jr. 2003. “Why is there so Little Money in US Politics?” Journal of Economic Perspectives. 17(1): 105–130.

>>>>

Since the 1970s, the U.S. Supreme Court has maintained that nearly all limits on political spending violate the first amendment’s protection of free speech. In its 1976 _Buckley v. Valeo_ decision, the Court laid out only two admissible justifications for limiting campaign donations: To prevent corruption or the appearance of corruption. But do campaign finance limits actually prevent corruption or its appearance? As current challenges to contribution limits wind their way through federal courts, the answer to this question will inform the Supreme Court’s decision to uphold or strike down remaining limits on political campaign contributions. Using state-level data from 1990-2012 on contribution limits, corruption convictions, and media mentions of corruption, this paper employs linear panel regressio to test whether campaign contribution limits are associated with lower levels of corruption convictions or media mentions of corruption. These methods find associations between corruption convictions and the presence of limits on donations to political action committees (PACs), the amount of those limits, and the presence of limits on donations to parties; individual donation limits do not prove associated with either measure of corruption.[^SPSA]

@@

```{r Barber summary stats latex, results="asis",eval=T}
stargazer(as.data.frame(subset(BarberNAs[,3:6])), digits=0, type="latex", title="Descriptive Statistics for State Level Campaign Finance Limits", covariate.labels = c("Individual Limits","Individual-to-Party Limits","Party Limits", "PAC Limits"), header=F, 
          notes = "Notes: 'N' equals number of state-years (out of n=1150) in which that type of limit is present") 
```

@@

The fourth data set provides controls for the panel model. In their 2012 work examining variation in prosecutorial resources, Alt and Lassen follow Glaeser and Saks (2006) in controlling for income and education levels, size of government, legislature control, and urbanization (see Appendix A). Alt and Lassen's data set runs from 1976-2004. When included in the second and third models, this limits the analysis to the years from 1990-2004 and n=720.

@@

#### Corruption Convictions Index versus campaign contribution limits in a given state-year: 
$(log)Convictions = \alpha_{state} + \\ \hspace{3.2cm} \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}\times{indiv.limit} + \\ \hspace{3.2cm} \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}\times{pac.limit} + \\ \hspace{3.2cm} \beta_{5}{indiv-to-party.dummy} + \beta_{6}{indiv-to-party.dummy}\times{indiv-to-party.limit} + \\ \hspace{3.2cm} Controls\times\gamma + \epsilon$ <!---->

#### Corruption Reflections Index versus campaign contributions in a given state-year: 
$(log)Reflections = \alpha_{state} + \\ \hspace{3.1cm} \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}\times{indiv.limit} + \\ \hspace{3.1cm} \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}\times{pac.limit} + \\ \hspace{3.1cm} \beta_{5}{indiv.to.party.dummy} + \beta_{6}{indiv.to.party.dummy}\times{indiv.to.party.limit} + \\ \hspace{3.1cm} Controls\times\gamma + \epsilon$

##Results 
The results of the panel regressions reveal multiple correlations between state-level campaign limits and Corruption Convictions; and one correlation between those limits and the Corruption Reflections Index.

The first set of models (Table 3) measures the association of various campaign contribution limits with the Corruption Convictions Index. The first model includes only control variables; the second model adds in campaign finance limit variables. The third layers in fixed effects at the state level, fixed time effects, and logged study variables; the fourth removes fixed effects but maintains the logged variables. Not included here are: models with random effects, models with unlogged dependent variables, and models with other combinations of fixed effects and variable transformations. The resulting models identify correlations between the CCI and the existence individual-to-party limits: The presence of such limits is associated with _greater_ corruption as measured by convictions. In Model 2, with unlogged independent variables, both the presence and amount of limits on PAC contributions to campaigns is associated with lower levels of corruption measured in terms of convictions.

The second set of models (Table 4) walks through the same progression of models, measuring the association of various campaign contribution limits and the Corruption Reflections Index (CRI). Model 4, which includes logged independent and dependent variables but not fixed effects, demonstrates that the presence of individual-to-party limits is associated with lower levels of corruption as measured by media mention of corruption. As with the CCI models in Table 3, the presence and amount of PAC limits, when unlogged, are associated with lower levels of corruption reflections.

<!--also fails to find a relationship between state-level campaign contribution limits and media mentions of corruption as measured by the Corruption Reflections Index, with one exception: The presence of limits on what an individual can give to a party is associated with a 0.11 point decline in the Corruption Reflections Index. The Corruption Reflections Index operates on a scale of zero to one (with a few outlying exceptions), indicating that the presence of individual-to-party limits is associated with a 11% decrease in the index. -->

@@

cci.log.iv.fixed.time <- plm(log(CCI+1) 
           ~ log(ind_limits_2010)*ind_limits_dummy 
           + log(ind2pty_limits_2010)*ind2pty_limits_dummy 
           + log(pac_limits_2010)*pac_limits_dummy
           + jdiv  # Divided government 
           # + bindingonetermlimit # Binding one-term limit 
           # + bindingtwotermlimit # Binding two-term limit 
           # + rpcinc_annual_new # Real per capita income ($1000)
           + eopop # AUSAs per million population
           # + unemp # Unemployment 
           # + citi6006 # Citizen ideology measure 
           + high_school + # Percent high school graduates
           + rgenrevpc # Real per capita gov revenues ($1000)
           # + men_ineqincwag # Inequality: Male wages
           # + grelimp # Relative government wages
           + urbanization_2 # Urbanization 
           + logpop, # Log of population (millions)
           data = AltBarber, 
           model="within",
           effect="twoways")

#### Single-variable models ####
cci.ind <- plm(
           log(CCI+1) ~ 
           log(ind_limits_2010)*ind_limits_dummy + 
           #log(ind2pty_limits_2010)*ind2pty_limits_dummy + 
           #log(pac_limits_2010)*pac_limits_dummy + 
           jdiv  # Divided government
           # + bindingonetermlimit # Binding one-term limit
           # + bindingtwotermlimit # Binding two-term limit
           # + rpcinc_annual_new # Real per capita income ($1000)
           + eopop # AUSAs per million population
           # + unemp # Unemployment
           # + citi6006 # Citizen ideology measure
           + high_school + # Percent high school graduates
           + rgenrevpc # Real per capita gov revenues ($1000)
           # + men_ineqincwag # Inequality: Male wages
           # + grelimp # Relative government wages
           + urbanization_2 # Urbanization
           + logpop, # Log of population (millions)
           data = AltBarber,
           model="pooling")

cci.ind2pty <- plm(
           log(CCI+1) ~ 
           #log(ind_limits_2010)*ind_limits_dummy + 
           log(ind2pty_limits_2010)*ind2pty_limits_dummy + 
           #log(pac_limits_2010)*pac_limits_dummy + 
           jdiv  # Divided government
           # + bindingonetermlimit # Binding one-term limit
           # + bindingtwotermlimit # Binding two-term limit
           # + rpcinc_annual_new # Real per capita income ($1000)
           + eopop # AUSAs per million population
           # + unemp # Unemployment
           # + citi6006 # Citizen ideology measure
           + high_school + # Percent high school graduates
           + rgenrevpc # Real per capita gov revenues ($1000)
           # + men_ineqincwag # Inequality: Male wages
           # + grelimp # Relative government wages
           + urbanization_2 # Urbanization
           + logpop, # Log of population (millions)
           data = AltBarber,
           model="pooling")

cci.pac <- plm(
           log(CCI+1) ~ 
           #log(ind_limits_2010)*ind_limits_dummy + 
           #log(ind2pty_limits_2010)*ind2pty_limits_dummy + 
           log(pac_limits_2010)*pac_limits_dummy + 
           jdiv  # Divided government
           # + bindingonetermlimit # Binding one-term limit
           # + bindingtwotermlimit # Binding two-term limit
           # + rpcinc_annual_new # Real per capita income ($1000)
           + eopop # AUSAs per million population
           # + unemp # Unemployment
           # + citi6006 # Citizen ideology measure
           + high_school + # Percent high school graduates
           + rgenrevpc # Real per capita gov revenues ($1000)
           # + men_ineqincwag # Inequality: Male wages
           # + grelimp # Relative government wages
           + urbanization_2 # Urbanization
           + logpop, # Log of population (millions)
           data = AltBarber,
           model="pooling")

stargazer(cci.ind,cci.ind2pty,cci.pac,type="text")

@@

```{r CCI models output, eval=T,results="asis"}
stargazer(
  cci.log.pars, 
  cci.log.iv, # F Stat down? 
  cci.log.iv.fixed.time, # F stat way down 
  cci.log.iv.log, # F Stat down further 
  #cci.log.iv.fixed, # AR2 Stat bottoms out 
  type="latex",
  #out = "collateral/test.htm",
  font.size = "small",
  header=FALSE, 
  column.sep.width = "-15pt", 
  digits = 2, digits.extra = 0, 
  no.space = TRUE,
  title = "Models of Contribution Limits and Corruption Convictions",
  dep.var.labels = "Corruption Convictions Index (logged)",
  covariate.labels=c("Individual limit (amount)",
                     "Individual limit (logged)",
                     "Individual limit (dummy)",
                     "Individual-to-party limit (amount)",
                     "Individual-to-party limit (logged)",
                     "Individual-to-party limit (dummy)",
                     "PAC limit (amount)",
                     "PAC limit (logged)",
                     "PAC limit (dummy)",
                     "Divided government",
                     "AUSAs per population (MMs)",
                     "Percent high school grads",
                     "Gov revenues per capita (1000s)",
                     "Urbanization",
                     "Log of population (MMs)"),
  add.lines = list(c(" ","Base Model","Full Model","Fixed Effects","Pooled"))
  )

@@

cri.log.iv.fixed.time <- plm(log(CRI+1) ~ 
             log(ind_limits_2010)*ind_limits_dummy 
           + log(ind2pty_limits_2010)*ind2pty_limits_dummy 
           + log(pac_limits_2010)*pac_limits_dummy
           # jdiv  # Divided government 
           # + bindingonetermlimit # Binding one-term limit 
           # + bindingtwotermlimit # Binding two-term limit 
           # + rpcinc_annual_new # Real per capita income ($1000)
           + eopop # AUSAs per million population
           # + unemp # Unemployment 
           + citi6006 # Citizen ideology measure 
           + high_school + # Percent high school graduates
           + rgenrevpc # Real per capita gov revenues ($1000)
           + men_ineqincwag # Inequality: Male wages
           # + grelimp # Relative government wages
           + urbanization_2 # Urbanization 
           + logpop, # Log of population (millions)
           data = AltBarber, 
           model="within",
           effect="twoways")

#### Single-variable models ####
cri.ind <- plm(
           log(CRI+1) ~ 
           log(ind_limits_2010)*ind_limits_dummy + 
           #log(ind2pty_limits_2010)*ind2pty_limits_dummy + 
           #log(pac_limits_2010)*pac_limits_dummy + 
           # jdiv  # Divided government 
           # + bindingonetermlimit # Binding one-term limit 
           # + bindingtwotermlimit # Binding two-term limit 
           # + rpcinc_annual_new # Real per capita income ($1000)
           + eopop # AUSAs per million population
           # + unemp # Unemployment 
           + citi6006 # Citizen ideology measure 
           + high_school + # Percent high school graduates
           + rgenrevpc # Real per capita gov revenues ($1000)
           + men_ineqincwag # Inequality: Male wages
           # + grelimp # Relative government wages
           + urbanization_2 # Urbanization 
           + logpop, # Log of population (millions)
           data = AltBarber,
           model="pooling")

cri.ind2pty <- plm(
           log(CRI+1) ~ 
           #log(ind_limits_2010)*ind_limits_dummy + 
           log(ind2pty_limits_2010)*ind2pty_limits_dummy + 
           #log(pac_limits_2010)*pac_limits_dummy + 
           # jdiv  # Divided government 
           # + bindingonetermlimit # Binding one-term limit 
           # + bindingtwotermlimit # Binding two-term limit 
           # + rpcinc_annual_new # Real per capita income ($1000)
           + eopop # AUSAs per million population
           # + unemp # Unemployment 
           + citi6006 # Citizen ideology measure 
           + high_school + # Percent high school graduates
           + rgenrevpc # Real per capita gov revenues ($1000)
           + men_ineqincwag # Inequality: Male wages
           # + grelimp # Relative government wages
           + urbanization_2 # Urbanization 
           + logpop, # Log of population (millions)
           data = AltBarber,
           model="pooling")

cri.pac <- plm(
           log(CRI+1) ~ 
           #log(ind_limits_2010)*ind_limits_dummy + 
           #log(ind2pty_limits_2010)*ind2pty_limits_dummy + 
           log(pac_limits_2010)*pac_limits_dummy + 
           # jdiv  # Divided government 
           # + bindingonetermlimit # Binding one-term limit 
           # + bindingtwotermlimit # Binding two-term limit 
           # + rpcinc_annual_new # Real per capita income ($1000)
           + eopop # AUSAs per million population
           # + unemp # Unemployment 
           + citi6006 # Citizen ideology measure 
           + high_school + # Percent high school graduates
           + rgenrevpc # Real per capita gov revenues ($1000)
           + men_ineqincwag # Inequality: Male wages
           # + grelimp # Relative government wages
           + urbanization_2 # Urbanization 
           + logpop, # Log of population (millions)
           data = AltBarber,
           model="pooling")

stargazer(cri.ind,cri.ind2pty,cri.pac,type="text")

@@

```{r CRI models output, eval=T,results="asis"}
stargazer(
  #cri, # started here, with other peoples' models 
  #cri.log, # Logged DVs; better results
  cri.log.pars, # Slimmed down model, no explanatory power lost 
  cri.log.iv, # Adding in IVs. AR2 up, F Stat down 
  cri.log.iv.fixed.time, # AR2 now negative 
  cri.log.iv.log, # Logging IVS. AR2 down, F Stat down 
  #cri.log.iv.fixed, # AR2 to zero 
  type="latex",
  #out = "collateral/test.htm",
  font.size = "small",
  header=FALSE, 
  column.sep.width = "-15pt", 
  digits = 2, digits.extra = 0, 
  no.space = TRUE,
  title = "Models of Contribution Limits and Corruption Reflections",
  dep.var.labels = "Corruption Reflections Index (logged)",
  covariate.labels=c("Individual limit (amount)",
                     "Individual limit (logged)",
                     "Individual limit (dummy)",
                     "Individual-to-party limit (amount)",
                     "Individual-to-party limit (logged)",
                     "Individual-to-party limit (dummy)",
                     "PAC limit (amount)",
                     "PAC limit (logged)",
                     "PAC limit (dummy)",
                     "AUSAs per million population",
                     "Citizen ideology measure",
                     "Percent high school graduates",
                     "Real per capita gov revenues (1000s)",
                     "Inequality: Male wages","Urbanization",
                     "Log of population (millions)"),
  add.lines = list(c(" ","Base Model","Full Model","Fixed Effects","Pooled"))
  )

@@

## Discussion
```{r skew,include=F}
library(moments) 
PAC_limits <- AltBarber$pac_limits_2010*AltBarber$pac_limits_dummy
skewness(PAC_limits) # 3.468 
PAC_limits_log <- log(AltBarber$pac_limits_2010)*AltBarber$pac_limits_dummy
skewness(PAC_limits_log) # -0.2467 
```

On their face, the models above support two tentative conclusions and present one puzzle: First, in none of the specifications above are limits on individuals' campaign contributions correlated with either corruption convictions or corruption reflections. This evidence of absence is not absence of evidence, of course, but consistent with the hypothesis that individual donations are not a primary source of political corruption.

The second tentative conclusion is that there is a yet-unspecified relationship between limits on PAC contributions and corruption. This is true in models in which _unlogged_ PAC limits are included in the models, but not when that variable, with a skew of 3.468, is logged. Given the non-normality of that variable, even when logged, it may be that a different transformation would more accurately specify these relationships. If those relationships hold, two possibilites may explain why limiting PAC donations might be associated with lower levels of corruption convictions and media coverage when individual limits are not. First, it may be that actors engaged enough in the political process to be able to corrupt public officials are likely to be entwined with, and work through, political action committees. Second, it may be that when corruption is routed through an institution such as a PAC, the number of people involved may make it more likely to be discovered, prosecuted and reported.

```{r corr,include=F}
cor.test(AltBarber$CRI,AltBarber$CCI) # 0.038
```

The puzzle in this data is the varying effects of limits on individual-to-party donations. The amount of those limits has no relationship in these models to either corruption convictions or reflections. But the presence of a limit is associated with _higher_ levels of corruption convictions and _lower_ levels of media coverage of corruption.[^SV] This suggests that states with limits on individual donations to political parties see more corruption, but less reporting on those convictions.

[^SV]: These relationships remain robust to changes in model specification, including when other donation limit variables are removed from the model.

What are the legal and policy implications of these results? The Supreme Court presently equates political donations with political speech, meaning that it is protected by the first amendment, but that preventing corruption or its appearance in the political system is so important that first amendment rights can be abridged to ensure it. For the Court, no other justification--including creating a more informed electorate, or stimulating more competitive elections, or equality of financial participation in elections--is an important enough concern that we should limit political speech in the form of campaign donations. The results above suggest that state-level restrictions on donations from individuals may not be demonstrably associated with lower corruption, but that other types of donation limits (on contributions from PACs to campaigns, and from individuals to parties) may indeed be associated with lowering corruption. Such results might allow for courts to be more open to the possibility of restricting donations to and from organized groups such as PACs and parties, without having to restrict individual donations and participation in the electoral process.

<!--In order to make this anti-reform argument, some important limitations must be dealt with. First, the Corruptions Conviction Index used above has multiple issues, as summarized above. Second, Dincer and Johnston’s Corruption Reflections Index, while a worthy effort, needs to be developed further. It relies on a single news source; a second version could examine state-level reporting, or include outlets from across the political spectrum. Second, the Corruption Reflections Index carries with it the assumption that media mentions are a mere reflection of corruption, whereas other work has demonstrated that media reporting on corruption has its own biases, and its own effects on perceptions of corruption. Further research could more fully explore these relationships, including the manner in which public perceptions of corruption provide enabling or constraining environments for corruption itself. Given the importance of these limitations, all that can be concluded from the analysis above is that no link between contribution limits and corruption has been demonstrated with this data, not that no link exists.

@@

If Jim Bopp and other conservative legal scholars have their way, the Supreme Court will soon take a closer look at the logic laid out by their predecessors in 1976 in support of campaign contribution limits. Justice Thomas's comments in _McCutcheon v. FEC_ suggest that commitment to the Buckley v. Valeo structure is weakening, and not in the way that campaign finance reformers might hope. Despite effort, scholars have failed to provide compelling evidence of a link between campaign contribution limits and corruption as defined by the Court. The measures of corruption that academics have used to date have serious limitations. Yet if the Court decides the burden of proof is on those looking to restrict political spending on narrow corruption grounds, reform advocates worried about money in politics have a steep empirical hill to climb, and likely only a few short years to do it.-->

\newpage
## Appendix A: Descriptions and Descriptive Statistics of Control Variables 
In their 2012 paper "Enforcement and Public Corruption: Evidence from the American States," Glaeser and Saks make use of the following control variables, which we have included here:

@@

\newpage
## References 
<!--Add new authors (see Google doc) and data. R packages?-->
Ansolabehere, Stephen, John M de Figueiredo, and James M Snyder Jr. 2003. “Why is there so Little Money in US Politics?” Journal of Economic Perspectives. 17(1): 105–130.
